Treatment planning for HDR Brachytherapy

### 2015-03-29 Paper Seminar/isim_paper.tex
Fixed ref errors, did some beauty work (i.e. newpage after toc)
added bib stuff for LP

\title{Treatment planning for HDR Brachytherapy}
\date{March 30, 2015}
\author{S.~Elm \and
T.~Karthe \and
M.~E.~Schroeder \and
D.~Golebiewski \and
L.~Mordhorst}

@@

\tableofcontents

@@

\section{Linear Programming}
In Linear Programming an objective function and constraints are used to compute the optimal solution to a minimization or maximization problem, as described in [?]. The problem consists of a certain number of variables and a feasible region, which is defined by the contraints. 
Equation \eqref{eq:LPMatrix} shows the standard form of a linear problem. The objective function, modeled with \textit{c},  is to be minimized, while the constraints, modeled with \textit{A} and \textit{b}, are satisfied. The used algorithm yields a vector x for the optimal solution.

@@

For our problem we used CPLEX, an implementation of the simplex algorithm by IBM[?]. In simplex the feasible region is considered a polyhedron. The optimal solution must be in one of the vertices of the polyhedron. Simplex finds a start vertex and approaches the optimal solution by moving from vertex to vertex on an edge, until there is no better solution.
The constraints allow us a good modelling of the tumor, since we are able to define a constraint with certain limits for each body type.

@@

\bibliographystyle{plain}
\bibliography{lit}

>>>>

\title{Treatment planning for HDR Brachytherapy}
\date{March 30, 2015}
\author{S.~Elm \and
T.~Karthe \and
M.~E.~Schroeder \and
%D.~Golebiewski \and
L.~Mordhorst}

@@

\tableofcontents
\newpage

@@

\section{Linear Programming}
In Linear Programming an objective function and constraints are used to compute the optimal solution to a minimization or maximization problem, as described in [\cite{matprog}]. The problem consists of a certain number of variables and a feasible region, which is defined by the contraints. 
Equation \eqref{eq:LPMatrix} shows the standard form of a linear problem. The objective function, modeled with \textit{c},  is to be minimized, while the constraints, modeled with \textit{A} and \textit{b}, are satisfied. The used algorithm yields a vector x for the optimal solution.

@@

For our problem we used CPLEX, an implementation of the simplex algorithm by IBM[\cite{cplex}]. In simplex the feasible region is considered a polyhedron. The optimal solution must be in one of the vertices of the polyhedron. Simplex finds a start vertex and approaches the optimal solution by moving from vertex to vertex on an edge, until there is no better solution.
The constraints allow us a good modelling of the tumor, since we are able to define a constraint with certain limits for each body type.

@@

\newpage
\bibliographystyle{plain}
\bibliography{lit}
